### 2023-08-17 application.tex
section

Without loss of generality hence let us consider only \fi
We consider the case when $\Safe$ is semilinear
and $\Bad = S \setminus \Safe$ is semilinear too.
{\sc Resilience} asks whether $\Bad \subseteq \pred^*(\Safe)$.
We have $\post^*(\Bad) \setminus \Safe = \Bad$ by extension of $S \setminus \Safe = \Bad$.
Thus $\post^*(\Bad) = \Bad \cup (\Safe \cap \post^*(\Bad))$. Since $(\Safe \cap \post^*(\Bad)) \subseteq \pred^*(\Safe)$, we have
\[\post^*(\Bad) \subseteq \pred^*(\Safe) \quad iff \quad \Bad \subseteq \pred^*(\Safe).\]
Since it is decidable whether $\post^*(\Bad) \subseteq \pred^*(\Safe)$ when 
$\Bad$ and $\Safe$ are both semilinear~\cite{DBLP:journals/corr/abs-2207-02697}, 
{\sc Resilience} is decidable.
\end{proof}

@@

\begin{proof}
We deduce from Theorem 3.6 in \cite{DBLP:conf/rp/Schnoebelen10} that $\pred^*(\Safe)$ is a computable semilinear set if $\Safe$ is semilinear. Hence since the inclusion between two semilinear sets is decidable, we deduce that $\Bad \subseteq \pred^*(\Safe)$ is decidable if $\Bad$ is semilinear.
\end{proof}

@@

The above results concern only unbounded resilience. We consider now 
{\sc Bounded resilience} and {\sc $k$-resilience}, and focus on the length of
the path from $\Bad$ to $\Safe$
when $\Safe$ is downward-closed. Unfortunately, we have the following:
\alain{incohérence des notations: VASS ou vector addition system with states and plus bas seulement vector addition system ??? VAS ???}
\begin{proposition}
{\sc Bounded resilience} and {\sc $k$-resilience} never hold for vector addition system \alain{pas défini}when $\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.
\end{proposition}

@@

All configurations reachable from $\textbf{u}_k$ in $k$ or less steps are above $ \textbf{v}_{\Bad} $
and thus, are in $\Bad$, by upward-closedness.
Hence  $\Safe$ is not reachable from $\textbf{u}_k$ in $k$ or less steps  and {$k$-resilience} does not hold.
Since the reasoning hold for all $k \in \N$, {\sc Bounded-resilience} does not hold either.
\end{proof}

@@

From $k_0$ onwards,
$\Bad \setminus (\pred^{\leq k}(\uparrow q_{j_1}(\textbf{0}))\cup \ldots \cup \pred^{\leq k}(\uparrow q_{j_\ell}(\textbf{0}))= 
\Bad \setminus (\pred^{*}(\uparrow q_{j_1}(\textbf{0})) \cup \ldots \pred^{*}(\uparrow q_{j_\ell}(\textbf{0})) )$
is stationnary. 
If the set is finite then we stop the procedure once we have checked for every element
whether it is possible to reach $\Safe$ from it.
If it is possible to reach $\Safe$ from every element then {\sc $k_m$-resilience}
hold
for $k_m = \max(k_0, k_{\pi})$ with 
$k_{\pi}$ the maximum of the length of the paths from 
$\Bad \setminus (\pred^{\leq k_0}(\uparrow q_{j_1}(\textbf{0}))\cup \ldots \cup \pred^{\leq k_0}(\uparrow q_{j_\ell}(\textbf{0}))$ to $\Safe$.
If it is infinite then
for every $k \in \N$,
$k$-resilience does not hold, 
and we eventually find a witness that $k$-resilience does not hold.
Indeed, 
if
$\Bad \setminus (\pred^{*}(\uparrow q_{j_1}(\textbf{0})) \cup \ldots \cup \pred^{*}(\uparrow q_{j_\ell}(\textbf{0})) )$
is
infinite
then
there exists an element of the form $q(\textbf{u} )$
with $\textbf{u} > \textbf{v}_{\Bad} + (k+1) \cdot (c_{\max}, \ldots, c_{\max})$ 
that is in $\Bad$ but not in any of the $\pred^{\leq k}(\uparrow q_{j_i}(\textbf{0}))$,
and hence from which it is not possible at all to reach
$\Safe$ in $k$ or less steps.
\end{proof}

>>>>

Without loss of generality hence let us consider only \fi
We consider the case when $\Safe$ is semilinear
and $\Bad = S \setminus \Safe$ is semilinear too.
{\sc Resilience} asks whether $\Bad \subseteq \pred^*(\Safe)$.
We have $\post^*(\Bad) \setminus \Safe = \Bad$ by extension of $S \setminus \Safe = \Bad$.
Thus $\post^*(\Bad) = \Bad \cup (\Safe \cap \post^*(\Bad))$. Since $(\Safe \cap \post^*(\Bad)) \subseteq \pred^*(\Safe)$, we have
\[\post^*(\Bad) \subseteq \pred^*(\Safe) \quad iff \quad \Bad \subseteq \pred^*(\Safe).\]
Since it is decidable whether $\post^*(\Bad) \subseteq \pred^*(\Safe)$ when 
$\Bad$ and $\Safe$ are both semilinear~\cite{DBLP:journals/corr/abs-2207-02697}, 
{\sc Resilience} is decidable. \qed
\end{proof}

@@

\begin{proof}
We deduce from Theorem 3.6 in \cite{DBLP:conf/rp/Schnoebelen10} that $\pred^*(\Safe)$ is a computable semilinear set if $\Safe$ is semilinear. Hence since the inclusion between two semilinear sets is decidable, we deduce that $\Bad \subseteq \pred^*(\Safe)$ is decidable if $\Bad$ is semilinear. \qed
\end{proof}

@@

The above results concern only unbounded resilience. We consider now 
{\sc Bounded resilience} and {\sc $k$-resilience}, and focus on the length of
the path from $\Bad$ to $\Safe$
when $\Safe$ is downward-closed. Unfortunately, we have the following:
\alain{incohérence des notations: VASS ou vector addition system with states and plus bas seulement vector addition system ??? VAS ???}
\begin{proposition}
{\sc Bounded resilience} and {\sc $k$-resilience} never hold for vector addition system when $\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.
\end{proposition}

@@

All configurations reachable from $\textbf{u}_k$ in $k$ or less steps are above $ \textbf{v}_{\Bad} $
and thus, are in $\Bad$, by upward-closedness.
Hence  $\Safe$ is not reachable from $\textbf{u}_k$ in $k$ or less steps  and {$k$-resilience} does not hold.
Since the reasoning hold for all $k \in \N$, {\sc Bounded-resilience} does not hold either.
\qed
\end{proof}

@@

From $k_0$ onwards,
$\Bad \setminus (\pred^{\leq k}(\uparrow q_{j_1}(\textbf{0}))\cup \ldots \cup \pred^{\leq k}(\uparrow q_{j_\ell}(\textbf{0}))= 
\Bad \setminus (\pred^{*}(\uparrow q_{j_1}(\textbf{0})) \cup \ldots \pred^{*}(\uparrow q_{j_\ell}(\textbf{0})) )$
is stationnary. 
If the set is finite then we stop the procedure once we have checked for every element
whether it is possible to reach $\Safe$ from it.
If it is possible to reach $\Safe$ from every element then {\sc $k_m$-resilience}
hold
for $k_m = \max(k_0, k_{\pi})$ with 
$k_{\pi}$ the maximum of the length of the paths from 
$\Bad \setminus (\pred^{\leq k_0}(\uparrow q_{j_1}(\textbf{0}))\cup \ldots \cup \pred^{\leq k_0}(\uparrow q_{j_\ell}(\textbf{0}))$ to $\Safe$.
If it is infinite then
for every $k \in \N$,
$k$-resilience does not hold, 
and we eventually find a witness that $k$-resilience does not hold.
Indeed, 
if
$\Bad \setminus (\pred^{*}(\uparrow q_{j_1}(\textbf{0})) \cup \ldots \cup \pred^{*}(\uparrow q_{j_\ell}(\textbf{0})) )$
is
infinite
then
there exists an element of the form $q(\textbf{u} )$
with $\textbf{u} > \textbf{v}_{\Bad} + (k+1) \cdot (c_{\max}, \ldots, c_{\max})$ 
that is in $\Bad$ but not in any of the $\pred^{\leq k}(\uparrow q_{j_i}(\textbf{0}))$,
and hence from which it is not possible at all to reach
$\Safe$ in $k$ or less steps.
\qed
\end{proof}
